### 2019-08-28 manuscript/manuscript.tex
ms changes

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is the total effect of linked selection between the
initial generation $0$ and some later generation $t$, which can be varied to
see how this quantity grows through time. As with the temporal covariances, the
study design of \textcite{Barghi2019} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances with each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal

@@

@@

>>>>

@@

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is the total effect of linked selection between the
initial generation $0$ and some later generation $t$, which can be varied to
see how this quantity grows through time. As with the temporal covariances, the
study design of \textcite{Barghi2019} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances with each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal that
greater than $20\%$ of total variation in allele frequency change over 60
generations is directly the result of linked selection.

The replicate design of \textcite{Barghi2019-qy} also allows us to quantify
another covariance: the covariance in allele frequency change between replicate
populations experiencing convergent selection pressure. These between-replicate
covariances are created in the same way as temporal covariances are: neutral
alleles linked to a particular fitness background experience are expected to
have allele frequency changes in the same direction if the selection pressures
are similar. We measure this through a statistic similar to a correlation,
which we call the convergent correlation; this is the ratio of average
between-replicate covariance across all pairs to the average standard deviation
across all pairs of replicates,

\begin{align}
  \mathrm{cor}(\Delta p_s, \Delta p_t) = \frac{\E_{A\ne B} \left( \cov(\Delta p_{s,A}, \Delta p_{t,B}) \right)}{\E_{A\ne B} \left( \sqrt{\var(\Delta p_{s,A}) \var(\Delta p_{t,B})} \right)}
\end{align}
%
where $A$ and $B$ here are two replicate labels.

We've calculated the convergent correlation for all rows of the replicate
covariance matrices, which unlike temporal covariance matrices have diagonal
elements that are also covariances (e.g. $\cov(\Delta p_{t,A}, \Delta
p_{t,B})$). Like temporal covariances, we visualize these through time (Figure
\ref{fig:figure-2} A), with each line representing the convergent correlation
from a particular reference generation $s$ as it varies with $t$ (shown on the
x-axis). In other words, each of the colored lines corresponds to the like
colored row of the convergence correlation matrix (upper left in Figure
\ref{fig:figure-2} A). We find these decay very quickly, from an initial
convergence correlation coefficient of about 0.1 (block bootstrap confidence
intervals XXX; see the note in Supplementary Material XXX why these are so
narrow), to around 0.01 within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate populations of
\emph{Drosophila simulans} for 14 generations in a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (p <
XXX, estimated via block bootstrap). We estimate the convergent correlation
coefficient across these replicates as 0.36 ($95\%$ block-bootstrap confidence
interval $[0.31, 0.40]$).

Second, we reanalyzed the Longshanks selection experiment, which selected for
longer tibiae length relative to body size in mice, leading to a response of
selection of about 5 standard deviations over the course of twenty generations
\parencite{Castro2019-uk}. This study includes two independent selection lines,
Longshanks 1 and 2 (LS1 and LS2), and an unselected control line (Ctrl).
Consequently, this selection experiment offers a useful control to test our
between-replicate covariances: we expect to see positive between-replicate
covariance in the comparison between the two Longshanks selection lines, but
not between the two pairwise comparisons between the control line and the two
Longshanks lines. We find that this is the case (Figure \ref{fig:figure-2} C),
with the two Longshanks comparisons to the control line not being significantly
different from zero, while the comparison between the two Longshanks line is
statistically significantly different from zero (CIs XXX).

Paragraph about large effect loci.

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed, some temporal covariances appeared to become negative at future
timepoints, a pattern that could be caused by advantageous fitness backgrounds
later becoming disadvantageous. The underlying causes could include
frequency-dependent selection, recombination disassociating beneficial and
deleterious alleles in repulsion linkage disequilibrium, or an environmental
change in the direction of selection. Thus far, our analysis has used
covariances averaged across the entire genome. Averaging over such large
numbers of loci is necessary to detect a signal of covariance in allele
frequency changes when both drift (inflated in evolve-and-sequence studies
which use small population sizes) and sampling variance can create spurious
covariances. However, the cost of using genome-wide covariances is that the
signal from regions harboring more additive genetic variance may be washed out
by noise. This is especially the case with detecting shifts in selection, which
are likely to be localized depending on the average effect of a region. To
address this limitation,
